Crowdy: Social Crowd Visualization

### 2011-04-28 docs/crowdy_gui.tex

\begin{figure}
\centering
\epsfig{file=img/TimelineView.eps, width= 250pt }
\caption{Timeline View}
\label{fig:Timeline View}
\end{figure}

\begin{figure}
\centering
\epsfig{file=img/CrowdViewInTimeline.eps, width= 250pt }
\caption{Crowd View In Timeline}
\label{fig:CrowdViewInTimeline}
\end{figure}

We apply the Simile Timeline library which is developed by MIT's Computer
Science and Artificial Intelligence Laboratory. The timeline as shown in figure \ref{fig:TimelineView} shows all of the
crowds at a given time span.  The timeline allows the analyst to zoom in on a
specific time, and move forward and backward thorough time.  The visualization
shows how long the crowd lasts, and the size of the crowd. We may make the
crowd taller or shorter based on the size of the crowd.  We will also display a
few keywords from each crowd. After a crowd in the timeline is clicked, a pop up ``Crowd View'' window will show the detailed information of this particular crowd (Figure \ref{}).

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{imgs/TimeLineView.png}
\caption{Timeline View}
\label{fig:TimelineView}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{imgs/CrowdViewInTimeLine.png}
\caption{Crowd View In Timeline}
\label{fig:CrowdViewInTimeline}
\end{figure}

We apply the Simile Timeline library which is developed by MIT's Computer
Science and Artificial Intelligence Laboratory. The timeline as shown in figure \ref{fig:TimelineView} shows all of the
crowds at a given time span.  The timeline allows the analyst to zoom in on a
specific time, and move forward and backward thorough time.  The visualization
shows how long the crowd lasts, and the size of the crowd. We may make the
crowd taller or shorter based on the size of the crowd.  We will also display a
few keywords from each crowd. After a crowd in the timeline is clicked, a pop up ``Crowd View'' window will show the detailed information of this particular crowd (Figure \ref{fig:CrowdViewInTimeline}).
